Novel crystallization pathway\\and formation of ``colloidal rain'' during viscoelastic phase separation

### 2015-08-07 crystal_gel_letter.tex
network structure different from the original phase separation pattern

\begin{abstract}
{
Colloidal gels form when spinodal phase separation is interrupted by the glass transition~\cite{lu2008gelation}. It has been shown that crystallization can equivalently interrupts the phase separation by freezing the existing network. However the particle-level details of this process have not yet been confirmed experimentally.
Here we show by confocal measurements that crystals nucleate inside the dense branches of a gel, and grow by evaporation of the liquid network and direct condensation of the gas phase on the surface of the crystals. This process represents the colloidal analogue of the Bergeron process~\cite{glickman2000glossary}, i.e. ice crystals formation that occurs in mixed phase clouds and is at the origin of rain. Our \emph{colloidal rain} gives us full experimental access to the kinetic pathway of this phenomenon important for climate science.
We argue that states similar to colloidal rain can form as the result of the gas-liquid phase separation of crystallizable components, such as monoatomic and molecular systems, whose dynamics is slow enough to induce viscoelastic phase separation, but fast enough to prevent immediate vitrification.
}
\end{abstract}

>>>>

\begin{abstract}
{
Colloidal gels form when spinodal phase separation is interrupted by the glass transition~\cite{lu2008gelation}. It has been shown that crystallization may equivalently interrupt the phase separation by freezing the dense phase. However the particle-level details of this process have not yet been confirmed experimentally.
Here we show by confocal microscopy measurements that crystallisation leads to a network structure different from the original phase separation pattern. Crystals nucleate inside the liquid network, and grow past it by direct condensation of the gas phase on their surface, driving evaporation of nearby liquid.
This process represents the colloidal analogue of the Bergeron process~\cite{glickman2000glossary}, i.e. ice crystals formation that occurs in mixed phase clouds and is at the origin of rain. Our \emph{colloidal rain} gives us full experimental access to the kinetic pathway of this phenomenon important for climate science.
We argue that states similar to colloidal rain can form as the result of the gas-liquid phase separation of crystallizable components, such as monoatomic and molecular systems, whose dynamics is slow enough to induce viscoelastic phase separation, but fast enough to prevent immediate vitrification.
}
\end{abstract}
